---
title: "hw04_couBC"
author: "CouBC"
date: '2018-10-07'
output: github_document
---

#Task 1 - Data Re-Shaping

In Window functions, we formed a tibble with 24 rows: 2 per year, giving the country with both the lowest and highest life expectancy (in Asia). Take that table (or a similar one for all continents) and reshape it so you have one row per year.

First, I load gapminder and tidyverse.

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(gapminder))
```

##I use the same specified tibble

```{r}
Asia_lifeExp <- gapminder %>%
  filter(continent == "Asia") %>%
  select(year, country, lifeExp) %>%
  group_by(year) %>%
  filter(min_rank(desc(lifeExp)) < 2 | min_rank(lifeExp) < 2) %>% 
  arrange(year) %>%
  print(n = Inf)
```



```{r}
Asia_untidy <- Asia_lifeExp %>% 
  spread(key = country, value = lifeExp)
Asia_untidy
```
 
 
 

#Task 2: 
Create your own cheatsheet patterned after Jenny’s but focused on something you care about more than comics.

You will likely need to iterate between your data prep and your joining to make your explorations comprehensive and interesting. For example, you will want a specific amount (or lack) of overlap between the two data.frames, in order to demonstrate all the different joins. You will want both the data frames to be as small as possible, while still retaining the expository value


```{r}
places_visited <- "
city, country, beach
  Tokyo, Japan, no
  Dubai, United Arab Emirates, yes
  Istanbul, Turkey, yes
  Rome, Italy, no
  San Antonio, United States, no
  Merida, Mexico, no
"

places_visited <- read_csv(places_visited, skip = 1)
places_visited

airports <- "
airports, country, airport_quality
  Narita, Japan, 4
  Dubai, United Arab Emirates, 6
  Ataturk, Turkey, 2
  Leonardo da Vinci, Italy, 3
  San Antonio, United States, 1
  Schiphol, Netherlands, 5
"
airports <- read_csv(airports, skip = 1)
airports
```
##left_join(places_visited, airports)

```{r}


lj_pa <- left_join(places_visited, airports) %>% 
  knitr::kable()
lj_pa

#with left join places_visited then airports, I am missing Schiphol airport (Netherlands) from the airports table. This left_join is matched by 'country'.
```

## left_join(airports, places_visited)

```{r}

lj_ap <- left_join(airports, places_visited) %>% 
knitr::kable()

lj_ap

#with left_join airport first, I retain Schiphol Airport (Netherlands) but lose Merida, Mexico as a place visited. Interpretation wise, this is an accurate depiction of my travel history as I've been to Schiphol airport but never been to Amsterdam. 
```
##right_join(places_visited, airports)

```{r}
rj_pa <- right_join(places_visited, airports) %>% 
knitr::kable()

rj_pa

# similar to left_join, I lose a bit of information. In Right_join(places_visited, airports) I lose out on visiting Merida, Mexico because I did not fly there. 
```

##right_join(airports, places_visited)

```{r}
rj_ap <- 
  right_join(airports, places_visited)  %>% 
knitr::kable()

rj_ap
#Here it depicts that I've been to Merida, Mexico but gives no quality of rating of airport.

```
##inner_join(places_visited, airports)

```{r}
ij_pa <- inner_join(places_visited, airports) %>% 
knitr::kable()

ij_pa

#Inner_join retains only rows in both sets. Here I miss out on Merida and Schiphol Airport
```

## inner_join(airports, places_visited)


```{r}
ij_ap <- inner_join(airports, places_visited) %>% 
knitr::kable()
ij_ap

#Similarly, I miss out on Merida and Schiphol Airport
```

##semi_join(places_visited, airports)

```{r}
sj_pa <- semi_join(places_visited, airports) %>% 
knitr::kable()
sj_pa

#in semi-join - only rows that have a match in places_visited and airports are retained, losing columns re: airport and airport quality
```

##semi_join(airports, places_visited)

```{r}
sj_ap <- semi_join(airports, places_visited) %>% 
knitr::kable()
sj_ap

#Here I lose out on city and beach columns.
```

##full_join(places_visited, airports)

```{r}
fj_pa <- 
full_join(places_visited, airports) %>% 
knitr::kable()
fj_pa

#full_join lets me retain the data from all rows and all values
```

##full_join(airports, places_visited)

```{r}
fj_ap <- 
  full_join(airports, places_visited) %>% 
knitr::kable()
fj_ap

#similar to previous full-join with airport table data displayed first, retains all available rows and values
```

##anti_join(places_visited, airports)

```{r}
aj_pa <-
anti_join(places_visited, airports) %>% 
knitr::kable()

aj_pa

#Anti_join only retains the rows that do not have a match in airports, in which case, this is Merida. I hypothesize that anti_join with airports first will produce Schiphol
```

##anti_join(airports, places_visited)

```{r}
aj_ap <- anti_join(airports, places_visited) %>% 
knitr::kable()
aj_ap 


#anti_join can be useful to identify/extricate non-matching rows between tables
```




